Sky Tomography for 3D Aerosol Distribution Recovery

### 2013-07-27 article.tex
bookmark

%
% Some new commands I use in this text
%
% Note:
% Nice curly font is {\bm{\mathcal{D}}}
%
\newcommand{\OpSphere}{\mathbfcal{S}}
\newcommand{\OpRot}{\mathbfcal{R}}
%\newcommand{\OpDistance}{\mathbfcal{D}}
\newcommand{\OpDistance}{\bm{D}}
\newcommand{\OpCumsum}{\mathbfcal{C}}
\newcommand{\OpInt}{\mathbfcal{I}}
\newcommand{\OpCamera}{\mathbfcal{P}}
\newcommand{\Mask}{\mathbfcal{M}}
\newcommand{\Laplacian}{\mathbfcal{L}}
\newcommand{\OpDiag}[1]{\mathrm{diag}\left\{#1\right\}}
\newcommand{\Grad}[1]{\bm{\triangledown_{#1}}}
\newcommand{\abbrev}[1]{\rm{#1}}
\newcommand{\argmin}{\mathrm{arg}\min}
\newcommand{\curly}[1]{\left\{#1\right\}}
\newcommand{\roundy}[1]{\left(#1\right)}
\newcommand{\recty}[1]{\left[#1\right]}
\newcommand{\PartDeriv}[2]{\frac{\partial{#1}}{\partial{#2}}}
\newcommand{\vect}[1]{\bm{#1}}
\newcommand{\mat}[1]{\bm{#1}}
\newcommand{\transpose}[1]{{#1}^\intercal}
\newcommand{\derivsym}[1]{\,d{#1}}
\newcommand{\yoavcomment}[1]{}
\renewcommand{\yoavcomment}[1]{#1} % Comment to remove images

@@

Any voxel generally contains both air molecules and aerosols.  We
assume that within any voxel, the molecular parameters $\{ \beta^{\rm
  air}(k),\alpha^{\rm air}(k)\}$ and the aerosol parameters $\{
\sigma^{\rm aerosol}(k),\varpi^{\rm aerosol}(k), n(k),g(k)\}$ are constants, e.g., corresponding to the value
at each voxel center.  Following \cref{eq:tau}, the optical depth
between the TOA and voxel $k$ is
\begin{equation}
  \tau_{\rm SR}(k)= \sum_{q \in[{\rm SR},k]} \beta(q) l_{\rm SR}(q) \;\;.
  \label{eq:lSRn}
\end{equation}
We can write \cref{eq:lSRn} using matrix notation, $\vect{\tau}_{\rm
  SR}=\OpDistance^{\mathrm{Sun \rightarrow voxel}} \vect{\beta}$,
where $\vect{\tau}_{\rm SR}$ and $\vect{\beta}$ are column stack
vector representations of $\tau_{\rm SR}(k)$ and $\beta(q)$,
respectively. Similarly, the optical depth along a LOS to voxel $k$ is
expressed by element $k$ of $\vect{\tau}_{{\rm LOS}_c} =
\OpDistance^{\mathrm{voxel \rightarrow cam}} \vect{\beta}$ Here
$\vect{\tau}_{{\rm LOS}_c}$ is a column stack vector representation of
$\tau_{{\rm LOS}_c}(k)$.  The SR and LOS paths joining at each voxel
can form a single path from the TOA to camera $c$, yielding
\begin{equation}
  {\bm D}_c=
  {\bm D}^{\mathrm{Sun \rightarrow voxel}}+
  {\bm D}^{\mathrm{voxel \rightarrow cam}}_c
  \quad\text{ and }\quad
  \vect{\tau}_c=
  \vect{\tau}_{\rm SR}+
  \vect{\tau}_{{\rm LOS}_c}
  \;\;.
  \label{eq:D_tau_total}
\end{equation}

We discern between air molecules and other aerosols and therefore
write $ \vect{\tau}_c= \vect{\tau}_c^{\rm air} + \vect{\tau}_c^{\rm
  aerosol}$.  Using \cref{eq:rayleighbeta} for $\beta^{\rm air}$ in
all voxels, the vector $\vect{\tau}_c^{\rm air}$ is fixed. Thus
$\vect{\tau}_c^{\rm air}$ can be calculated once, per sun zenith
angle. Given \cref{eq:extinctc}, the total optical depths
corresponding to LOSs (of camera $c$) and SRs that cross all voxels
comprise the vector
\begin{equation}
  \vect{\tau}_c= \vect{\tau}_c^{\rm air}
  + {\bm D}_c (\vect{\sigma} \odot {\bm n})
  \;\;.
  \label{eq:tautotal}
\end{equation}
where the operator $\odot$ denotes the Hadamard (element-wise)
product. This vector depends on the variables $\vect{\sigma}$ and
${\bm n}$, the aerosol extinction and density at each voxel,
respectively.

@@

Per camera $c$ and voxel $k$, the lines $[{\rm SR},k]$ and $[{\rm
  LOS}_c,k]$ intersect at a fixed angle $\Phi^{\rm scatter}_c(k)$.
Column-stacking all voxels yields the vector representation of all
scattering angles in the domain, $\vect{\Phi}^{\rm scatter}_c$ per
camera $c$. Similarly, the single-scattering albdeos $\varpi^{\rm
  aerosol}$ in all voxels are stacked to vector $\vect{\varpi}$.
Using \cref{eq:alphabasic,eq:rayleighP}, the angular scattering
coefficients across the domain are expressed in vector form by
\begin{equation}
  \tilde{\vect{\alpha}}^{\rm air}_c =
  \vect{\beta}^{\rm air} \odot P^{\rm air}(\vect{\Phi}^{\rm scatter}_c)\;,\quad
  \tilde{\vect{\alpha}}^{\rm aerosol}_c = \vect{\varpi}\odot
  \vect{\sigma} \odot {\bm n} \odot P^{\rm aerosol}_{\bm
    g}(\vect{\Phi}^{\rm scatter}_c) \;.
  \label{eq:alpha_matrix}
\end{equation}
The vector ${\bm g}$ column-stacks the aerosol anisotropy parameter of
the phase function, in all voxels. This notation indicates a
parametric phase function as in \cref{eq:aerosol_scatter}.

@@

Compounding the attenuation of irradiance along both $[{\rm SR},k]$
and $[{\rm LOS}_c,k]$, and scattering by voxel $k$ towards the camera
(\cref{eq:beer-lambert,eq:betair,eq:tautotal}) the radiant power
contributed by the voxel is
\begin{equation}
  p_c(k)= L^{\rm TOA}
  [\tilde{\alpha}^{\rm air}_c(k) + \tilde{\alpha}^{\rm aerosol}_c(k)]
  \exp[-\tau_c(k)]
  \;\;,
  \label{eq:ick}
\end{equation}
where $L^{\rm TOA}$ is the radiance at the TOA. A column-stack vector
of all voxel contributions is
\begin{equation}
  {\bm p}_c= L^{\rm TOA}
  [\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm aerosol}_c]
  \odot \exp(-\vect{\tau}_c)
  \;\;.
  \label{eq:pc}
\end{equation}

A camera pixel collects light from a narrow cone in the
atmosphere. The cone contains or intersects some voxels, while being oblivious to all the rest~(\cref{fig:projection}b).
% \begin{figure}
%   \centering
%   \yoavcomment{\def\svgwidth{0.8\columnwidth}\input{images/light_transfer.pdf_tex}}
%   \caption{\small [a] Irradiance of voxel $k$ is attenuated by
%   voxels above it on a SR. The scattered radiance from voxel $k$ is
%   then attenuated by voxels below it on a LOS to camera $c$.  [b] An
%   image pixel captures light emanating in a cone in space. Voxels
%   that fully or partially fall in this cone are sensed by the
%   pixel.}
%   \label{fig:projection}
% \end{figure}
Overall, light power captured at a pixel is a weighted sum of the power
$p_c(k)$ from all voxels.  This sum is formulated by a matrix
operation over ${\bm p}_c$:
\begin{equation}
  {\bm i}_c= {\vect{\Pi}}_c{\bm p}_c
  \;\;,
  \label{eq:IcP}
\end{equation}
where ${\bm i}_c$ is the image, column-stacked to a
vector $N_{\rm pix}$ long.

Combining \cref{eq:tautotal,eq:pc,eq:IcP}, the captured image is thus
\begin{align}
  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \left\{
    (\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm
      aerosol}_c) \odot \exp\{-[\vect{\tau}_c^{\rm air} + {\bm D}_c
    (\vect{\sigma} \odot {\bm n})]\} \right\}
  \label{eq:bigIc}
\end{align}
We focus on situations where there is only a single
type of aerosol over a scene. Hence, the three-element vector
$[{\sigma}^{\rm aerosol},\varpi^{\rm aerosol},g]$ is uniform across
the scene, but the density distribution ${\bm n}$ is variable. Then,
\cref{eq:bigIc} degenerates to
\begin{align}
  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{
  [\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
    aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
    scatter}_c) \odot{\bm n} ]
  \odot
  \exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol} {\bm D}_c{\bm n})]
    \Big\} .
  \label{eq:bigIA}
\end{align}

@@

We seek to estimate the aerosol distribution. Most generally, this is the set
$\left\{{\bm n},\left\{\vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bm
        g}_{\lambda}\right\}_{\lambda}\right\}$
where some of the parameters depend on the spectral channel $\lambda$. Usually, however, a single aerosol type dominates a scene. Furthermore, we assume that the type of the aerosol above an area is known~\cite{Martonchik2009}. Hence, we focus on estimating the density distribution ${\bm n}$.

The recovery task is phrased as optimization of an objective function,
that fits the image-formation model (\cref{eq:bigIc,eq:bigIA}) to
$N_{\rm views}$ measured photographs $\{ {\bm i}^{\rm
  measured}_c\}_{c=1}^{N_{\rm views}}$:
\begin{equation}
  \label{eq:minobjectiveA}
  \hat{\bm n} =
  \argmin_{{\bm n}} F({\bm n})
\end{equation}
where
\begin{equation}
  \label{eq:objectiveA}
  F({\bm n})
  = \sum_{c=1}^{N_{\rm views}}
  \| \Mask \roundy{{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})}\|^2_2
  + \eta \Psi({\bm n})
\end{equation}
where $\Mask$ is a map that masks the areas around
the sun, which are overwhelmingly bright. %and the horizon.
%These regions are prone to dominant multiple scattering.
In Eq.~(\ref{eq:objectiveA}), $\Psi({\bm n})$ is a regularization term that expresses some prior knowledge on the distribution, while $\eta$ is a regularization weight.  Since aerosol distributions are usually fuzzy,
it can be beneficial that regularization be a {\em smoothness term}, which penalized energy in second order spatial derivatives (3D Laplacian). Hende, we use
\begin{equation}
  \label{eq:regularizer}
  \Psi({\bm n}) = \| \nabla^2{\bm n}\|^2_2 = \| \Laplacian{\bm n}\|^2_2
\end{equation}
where $\Laplacian$ is a matrix representation of the 3D \emph{Laplacian}
operator.

We solve~\cref{eq:minobjectiveA} using standard optimization tools.
The gradient of $F$ with respect to ${\bm n}$ is
\begin{align}
  \Grad{{\bm n}} F = -2\sum_{c=1}^{N_{\rm views}}
  \transpose{\left[{\bm J}_{{\bm i}_c}({\bm n})\right]} [{\bm i}^{\rm
    measured}_c - {\bm i}_c({\bm n})] + 2 \eta \transpose{\Laplacian}\Laplacian{\bm n} \;.
  \label{eq:gradient1}
\end{align}
Here the matrix ${\bm J}_{{\bm i}_c}({\bm n})$ is the Jacobian of the
vector ${\bm i}_c$ with respect to ${\bm n}$.  Element $(\Theta,k)$ of
this matrix differentiates the intensity in pixel ${\bm \Theta}$ (in
viewpoint $c$) with variation of the aerosol density at voxel $k$, i.e.,
$\partial i_c({\bm \Theta})/\partial{n(k)}$.  A
close-form expression of the Jacobian and its detailed derivation is
given in \cref{sec:gradient-derivation}.

>>>>

%
% Some new commands I use in this text
%
% Note:
% Nice curly font is {\bm{\mathcal{D}}}
%
\newcommand{\OpSphere}{\mathbfcal{S}}
\newcommand{\OpRot}{\mathbfcal{R}}
%\newcommand{\OpDistance}{\mathbfcal{D}}
\newcommand{\OpDistance}{\bm{D}}
\newcommand{\OpCumsum}{\mathbfcal{C}}
\newcommand{\OpInt}{\mathbfcal{I}}
\newcommand{\OpCamera}{\mathbfcal{P}}
\newcommand{\Mask}{\mathbfcal{M}}
\newcommand{\Laplacian}{\mathbfcal{L}}
%\newcommand{\OpDiag}[1]{\mathrm{diag}\left\{#1\right\}}
\newcommand{\OpDiag}[1]{\mathbb{D}\left\{#1\right\}}
\newcommand{\Grad}[1]{\bm{\triangledown_{#1}}}
\newcommand{\abbrev}[1]{\rm{#1}}
\newcommand{\argmin}{\mathrm{arg}\min}
\newcommand{\curly}[1]{\left\{#1\right\}}
\newcommand{\roundy}[1]{\left(#1\right)}
\newcommand{\recty}[1]{\left[#1\right]}
\newcommand{\PartDeriv}[2]{\frac{\partial{#1}}{\partial{#2}}}
\newcommand{\vect}[1]{\bm{#1}}
\newcommand{\mat}[1]{\bm{#1}}
\newcommand{\transpose}[1]{{#1}^\intercal}
\newcommand{\derivsym}[1]{\,d{#1}}
\newcommand{\yoavcomment}[1]{}
\renewcommand{\yoavcomment}[1]{#1} % Comment to remove images

@@

Any voxel generally contains both air molecules and aerosols.
We focus on situations where there is only a single type of aerosol over a scene. Hence, the three-element vector
$[{\sigma}^{\rm aerosol},\varpi^{\rm aerosol},g]$ is uniform across
the scene, but the density distribution ${\bm n}$ is variable. As a numerical approximation,
assume that within any voxel, the molecular parameters $\{ \beta^{\rm
  air}(k),\alpha^{\rm air}(k)\}$ and the aerosol density $n(k)$ are constants, e.g., corresponding to the value
at each voxel center.  Following \cref{eq:tau}, the optical depth
between the TOA and voxel $k$ is
\begin{equation}
  \tau_{\rm SR}(k)= \sum_{q \in[{\rm SR},k]} \beta(q) l_{\rm SR}(q) \;\;.
  \label{eq:lSRn}
\end{equation}
We can write \cref{eq:lSRn} using matrix notation, $\vect{\tau}_{\rm
  SR}=\OpDistance^{\mathrm{Sun \rightarrow voxel}} \vect{\beta}$,
where $\vect{\tau}_{\rm SR}$ and $\vect{\beta}$ are column stack
vector representations of $\tau_{\rm SR}(k)$ and $\beta(q)$,
respectively. Similarly, the optical depth along a LOS to voxel $k$ is
expressed by element $k$ of $\vect{\tau}_{{\rm LOS}_c} =
\OpDistance^{\mathrm{voxel \rightarrow cam}} \vect{\beta}$ Here
$\vect{\tau}_{{\rm LOS}_c}$ is a column stack vector representation of
$\tau_{{\rm LOS}_c}(k)$.  The SR and LOS paths joining at each voxel
can form a single path from the TOA to camera $c$, yielding
\begin{equation}
  {\bm D}_c=
  {\bm D}^{\mathrm{Sun \rightarrow voxel}}+
  {\bm D}^{\mathrm{voxel \rightarrow cam}}_c
  \quad\text{ and }\quad
  \vect{\tau}_c=
  \vect{\tau}_{\rm SR}+
  \vect{\tau}_{{\rm LOS}_c}
  \;\;.
  \label{eq:D_tau_total}
\end{equation}

We discern between air molecules and other aerosols and therefore
write $ \vect{\tau}_c= \vect{\tau}_c^{\rm air} + \vect{\tau}_c^{\rm
  aerosol}$.  Using \cref{eq:rayleighbeta} for $\beta^{\rm air}$ in
all voxels, the vector $\vect{\tau}_c^{\rm air}$ is fixed. Thus
$\vect{\tau}_c^{\rm air}$ can be calculated once, per sun zenith
angle. Given \cref{eq:extinctc}, the total optical depths
corresponding to LOSs (of camera $c$) and SRs that cross all voxels
comprise the vector
\begin{equation}
  \vect{\tau}_c= \vect{\tau}_c^{\rm air}
  + \sigma^{\rm aerosol} {\bm D}_c {\bm n}
  \;\;.
  \label{eq:tautotal}
\end{equation}

@@

Per camera $c$ and voxel $k$, the lines $[{\rm SR},k]$ and $[{\rm
  LOS}_c,k]$ intersect at a fixed angle $\Phi^{\rm scatter}_c(k)$.
Column-stacking all voxels yields the vector representation of all
scattering angles in the domain, $\vect{\Phi}^{\rm scatter}_c$ per
camera $c$. 
%Similarly, the single-scattering albdeos $\varpi^{\rm aerosol}$ in all voxels are stacked to vector $\vect{\varpi}$.
Using \cref{eq:alphabasic,eq:rayleighP}, the angular scattering
coefficients across the domain are expressed in vector form by
\begin{equation}
  \tilde{\vect{\alpha}}^{\rm air}_c =
      \vect{\beta}^{\rm air} \odot P^{\rm air}(\vect{\Phi}^{\rm scatter}_c)\;,
      \quad
%  \tilde{\vect{\alpha}}^{\rm aerosol}_c = \vect{\varpi}\odot
%  \vect{\sigma} \odot {\bm n} \odot P^{\rm aerosol}_{\bm
%    g}(\vect{\Phi}^{\rm scatter}_c) \;.
  \tilde{\vect{\alpha}}^{\rm aerosol}_c = 
       \varpi^{\rm aerosol} \sigma^{\rm aerosol} 
        {\bm n} \odot P^{\rm aerosol}_{\bm g}(\vect{\Phi}^{\rm scatter}_c) \;.
  \label{eq:alpha_matrix}
\end{equation}
%The vector ${\bm g}$ column-stacks the aerosol anisotropy parameter of
%the phase function, in all voxels. This notation indicates a
%parametric phase function as in \cref{eq:aerosol_scatter}.
Here the operator $\odot$ denotes the Hadamard (element-wise)
product.

@@

Compounding the attenuation of irradiance along both $[{\rm SR},k]$
and $[{\rm LOS}_c,k]$, and scattering by voxel $k$ towards the camera
(\cref{eq:beer-lambert,eq:betair,eq:tautotal}) the radiant power
contributed by the voxel is
\begin{equation}
  p_c(k)= L^{\rm TOA}
  [\tilde{\alpha}^{\rm air}_c(k) + \tilde{\alpha}^{\rm aerosol}_c(k)]
  \exp[-\tau_c(k)]
  \;\;,
  \label{eq:ick}
\end{equation}
where $L^{\rm TOA}$ is the radiance at the TOA. A column-stack vector
of all voxel contributions is
\begin{equation}
  {\bm p}_c= L^{\rm TOA}
  (\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm aerosol}_c)
  \odot \exp(-\vect{\tau}_c)
  \;\;.
  \label{eq:pc}
\end{equation}

A camera pixel collects light from a narrow cone in the
atmosphere. The cone contains or intersects some voxels, while being oblivious to all the rest~(\cref{fig:projection}b).
% \begin{figure}
%   \centering
%   \yoavcomment{\def\svgwidth{0.8\columnwidth}\input{images/light_transfer.pdf_tex}}
%   \caption{\small [a] Irradiance of voxel $k$ is attenuated by
%   voxels above it on a SR. The scattered radiance from voxel $k$ is
%   then attenuated by voxels below it on a LOS to camera $c$.  [b] An
%   image pixel captures light emanating in a cone in space. Voxels
%   that fully or partially fall in this cone are sensed by the
%   pixel.}
%   \label{fig:projection}
% \end{figure}
Overall, light power captured at a pixel is a weighted sum of the power
$p_c(k)$ from all voxels.  This sum is formulated by a matrix
operation over ${\bm p}_c$:
\begin{equation}
  {\bm i}_c= {\vect{\Pi}}_c{\bm p}_c
  \;\;,
  \label{eq:IcP}
\end{equation}
where ${\bm i}_c$ is the image, column-stacked to a
vector $N_{\rm pix}$ long.
Combining \cref{eq:tautotal,eq:pc,eq:IcP}, the captured image is thus
%\begin{align}
%  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \left\{
%    (\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm
%      aerosol}_c) \odot \exp\{-[\vect{\tau}_c^{\rm air} + {\bm D}_c
%    (\vect{\sigma} \odot {\bm n})]\} \right\}
%  \label{eq:bigIc}
%\end{align}
%We focus on situations where there is only a single
%type of aerosol over a scene. Hence, the three-element vector
%$[{\sigma}^{\rm aerosol},\varpi^{\rm aerosol},g]$ is uniform across
%the scene, but the density distribution ${\bm n}$ is variable. Then,
%\cref{eq:bigIc} degenerates to
\begin{align}
  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{
  [\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
    aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
    scatter}_c) \odot{\bm n} ]
  \odot
  \exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol} {\bm D}_c{\bm n})]
    \Big\} .
  \label{eq:bigIA}
\end{align}

@@

In this paper, we assume that the type of the aerosol above an area is known~\cite{Martonchik2009}. Hence, we focus on estimating the density distribution ${\bm n}$.
%Most generally, this is the set
%$\left\{{\bm n},\left\{\vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bm
%        g}_{\lambda}\right\}_{\lambda}\right\}$
%where some of the parameters depend on the spectral channel $\lambda$. 
%Usually, a single aerosol type dominates a scene. Furthermore, we assume that the type of the aerosol above an area is known~\cite{Martonchik2009}. Hence, we focus on estimating the density distribution ${\bm n}$.
At hand, we have $N_{\rm views}$ measured photographs 
 $\{ {\bm i}^{\rm measured}_c\}_{c=1}^{N_{\rm views}}$. The recovery task is phrased as
optimization of an objective function that fits the image-formation model to the measured photographs:
\begin{equation}
  \label{eq:minobjectiveA}
  \hat{\bm n} =
  \argmin_{{\bm n}} F({\bm n})
\end{equation}
where
\begin{equation}
  \label{eq:objectiveA}
  F({\bm n})
  = \sum_{c=1}^{N_{\rm views}}
  \| \Mask \roundy{{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})}\|^2_2
  + \eta \Psi({\bm n})
\end{equation}
where $\Mask$ is a map that masks the areas around
the sun, which are overwhelmingly bright. %and the horizon.
%These regions are prone to dominant multiple scattering.
In Eq.~(\ref{eq:objectiveA}), $\Psi({\bm n})$ is a regularization term that expresses some prior knowledge on the distribution, while $\eta$ is a regularization weight.  Since aerosol distributions are usually fuzzy,
it can be beneficial that regularization be a {\em smoothness term}, which penalized energy in second order spatial derivatives (3D Laplacian). Hende, we use
\begin{equation}
  \label{eq:regularizer}
  \Psi({\bm n}) = \| \nabla^2{\bm n}\|^2_2 = \| \Laplacian{\bm n}\|^2_2
\end{equation}
where $\Laplacian$ is a matrix representation of the 3D \emph{Laplacian}
operator.

We solve~\cref{eq:minobjectiveA} using standard optimization tools.
The gradient of $F$ with respect to ${\bm n}$ is
\begin{align}
  \Grad{{\bm n}} F = -2\sum_{c=1}^{N_{\rm views}}
  \transpose{\left[{\bm J}_{{\bm i}_c}({\bm n})\right]} [{\bm i}^{\rm
    measured}_c - {\bm i}_c({\bm n})] + 2 \eta \transpose{\Laplacian}\Laplacian{\bm n} \;.
  \label{eq:gradient1}
\end{align}
Here the matrix ${\bm J}_{{\bm i}_c}({\bm n})$ is the Jacobian of the
vector ${\bm i}_c$ with respect to ${\bm n}$.  Element $(\Theta,k)$ of
this matrix differentiates the intensity in pixel ${\bm \Theta}$ (in
viewpoint $c$) with variation of the aerosol density at voxel $k$, i.e.,
$\partial i_c({\bm \Theta})/\partial{n(k)}$.

We now detail the derivation of the Jacobian ${\bm J}_{{\bm i}_c}({\bm n})$. First, we provide some results relating to differentiation.  Let
$\vect{a}(\vect{n}),\vect{u}(\vect{n})$ be vector functions: each outputs a vector of
length $r$. Let $\mat{C}$ be a $r \times N_{\rm voxels}$ matrix, where $N_{\rm voxels}$ is the length of ${\bm n}$.
Then,
\begin{align}
  \label{eq:partial1}
  \PartDeriv{\transpose{\mat{C}} (\vect{a} \odot \vect{u})}{\vect{n}}
  = \left[ \PartDeriv{\vect{a}}{\vect{n}} \OpDiag{\vect{u}} +
    \PartDeriv{\vect{u}}{\vect{n}} \OpDiag{\vect{a}} \right] \mat{C}.
\end{align}
Here $\OpDiag{\vect{v}}$ is a conversion of a general vector $\vect{v}$
into a diagonal matrix, whose main diagonal elements correspond to the
elements of $\vect{v}$. Now, let
%\begin{align}
  $\vect{a}(\vect{n}) = \exp(-{\mat{C}}\vect{n})$,
%  \label{eq:example1}
%\end{align}
%In \cref{eq:example1},
where the exponent is element-wise (not raising an
operator to some power). Then
\begin{align}
  \label{eq:partial2}
  \PartDeriv{\vect{a}}{\vect{n}} &= - \transpose{\mat{C}} \,
  \OpDiag{\exp(-{\mat{C}}\vect{n})}.
\end{align}
Using \cref{eq:partial2},
\begin{align}
  \label{eq:partial4}
  \PartDeriv{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}{\bm D}_c {\bm n})]}
  {\vect{n}} &= - {\sigma}^{\rm aerosol}\transpose{\OpDistance_c} \,
  \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}{\bm D}_c {\bm n})]},
\end{align}
where $\vect{\tau}_c^{\rm air}$ is independent of ${\bm n}$. Using \cref{eq:partial1},
\begin{align}
  \label{eq:partial3}
  \PartDeriv{\, [\varpi^{\rm aerosol}\sigma^{\rm aerosol} P^{\rm
      aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm n}]}{\vect{n}}
  =
  \varpi^{\rm aerosol}\sigma^{\rm aerosol}\OpDiag{P^{\rm
      aerosol}_g(\vect{\Phi}^{\rm scatter}_c)}.
\end{align}
Based on \cref{eq:partial4,eq:partial1,eq:partial3} we derive the Jacobian of \cref{eq:bigIA}
in close-form,
\begin{align}
%  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}(\abbrev{A}-\abbrev{B})\abbrev{C}
  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}{\sigma}^{\rm aerosol}({\bf A}-{\bf B})
  \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
      aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
   ,
  \label{eq:gradient2}
\end{align}
where
%\begin{align}
%  \label{eq:gradient3}
%  {\bf A} &= \varpi^{\rm aerosol}
%  \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
%  {\bf B} &= \transpose{{\bm D}_c} %\nonumber\\
%%  & \;\;\;
%      \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
%      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
%      scatter}_c) \odot{\bm n}
%    ]}
%    %\nonumber \\
%  %\abbrev{C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
%   %   aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
%\end{align}
\begin{equation}
  \label{eq:gradient3}
  {\bf A} = \varpi^{\rm aerosol}
       \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)}
  ,\;\;\;
  {\bf B} = \transpose{{\bm D}_c}
      \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
      scatter}_c) \odot{\bm n}    ]}
\end{equation}
